Combine_results

### 2017-06-06 Code/1_Explore_Data.Rmd

```{r read_raw_data}
dat <- read.table("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/deaths-cause-6913.txt", header = F,sep="\t")
names(dat) <- c("State", "Age", "Sex", "Race", "COD", "Year", "Crude_Rate", "Count", "Population")
names(dat) <- c("state.n", "age.n", "sex.n", "race.n", "COD.n", "year.0", "crude.rate", "deaths", "population") 
# names and order of variables in the dataset are noted in the .dic dictionary file found in the same dir as the dataset.
```

@@

```{r write_data_to_csvs}
#save.image(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
write_csv(dat.clean, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.csv", col_names = T)
write_csv(dat.aggregated, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.csv", col_names = T)

@@

for(i in 1:length(included.states)) { 
  name = paste0('dat_clean_', included.states[i], '.csv')
  ds_temp = dat.clean[dat.clean$state == included.states[i], ]
  write.csv(ds_temp, file = paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Data/", name))
}
rm(ds_temp)
```

```{r save_specified_files}
# save(dat.clean, dat2, BlackWhite, BlackWhiteSmooth, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
#      list.age.decomp.tables5, list.cod.decomp.tables5, list.age.decomp.tables9, list.cod.decomp.tables9,
#      list.age.decomp.tables.smoothed, list.cod.decomp.tables.smoothed, list.cod.marginal.tables.smoothed,
#      non.zero.stratums, non.zero.stratums.smoothed, cod.contributions,
#      file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```

>>>>

```{r read_raw_data}
dat <- read.table("./Data/deaths-cause-6913.txt", header = F, sep="\t")
names(dat) <- c("State", "Age", "Sex", "Race", "COD", "Year", "Crude_Rate", "Count", "Population")
names(dat) <- c("state.n", "age.n", "sex.n", "race.n", "COD.n", "year.0", "crude.rate", "deaths", "population") 
# names and order of variables in the dataset are noted in the .dic dictionary file found in the same dir as the dataset.
```

@@

```{r write_data_to_csvs}
write_csv(dat.aggregated, path = "./dat_aggregated.csv", col_names = T)

@@

for(i in 1:length(included.states)) { 
  name = paste0('dat_clean_', included.states[i], '.csv')
  ds_temp = dat.clean[dat.clean$state == included.states[i], ]
  write.csv(ds_temp, file = paste0("./Data/", name))
}
rm(ds_temp)
```

### 2017-06-06 Code/3_combine_results.Rmd

**Combine results across the sets**
The analysis was run in 8 sets. In this file we combine the results and tidy the data for graph and presentation.

```{r initialize}
library(stringr)
library(dplyr)
source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

```{r}
included.states <- c("Alabama", "Arizona", "Arkansas", "California", "Colorado", "Connecticut",
"Delaware", "Florida", "Georgia", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky",
"Louisiana", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi",   
"Missouri", "Nebraska", "Nevada", "New Jersey", "New Mexico", "New York",
"North Carolina", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island",
"South Carolina",  "Tennessee", "Texas", "Virginia", "Washington", "Washington DC",
"West Virginia", "Wisconsin")

completed.states <- included.states
```

```{r combine_results_seed123}
age_cod_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_", completed.states[1], "_123.csv"))
age_decomp_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_decomp_", completed.states[1], "_123.csv"))
BlackWhite_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_", completed.states[1], "_123.csv"))
cod_decomp_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_marginal_", completed.states[1], "_123.csv"))
cod_change_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_change_", completed.states[1], "_123.csv"))

mortality.rates <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_", completed.states[1], "_123.csv"))
mortality.rates.diff <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_diff_", completed.states[1], "_123.csv"))

for(state_i in 2:length(completed.states)){

    age_cod_results <- rbind(age_cod_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_", completed.states[state_i], "_123.csv")))

    age_decomp_results <- rbind(age_decomp_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_decomp_", completed.states[state_i], "_123.csv")))

    BlackWhite_results <- rbind(BlackWhite_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_", completed.states[state_i], "_123.csv")))

    cod_decomp_results <- rbind(cod_decomp_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_marginal_", completed.states[state_i], "_123.csv")))

    cod_change_results <- rbind(cod_change_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_change_", completed.states[state_i], "_123.csv")))

  mortality.rates <- rbind(mortality.rates, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_", completed.states[state_i], "_123.csv")))

    mortality.rates.diff <- rbind(mortality.rates.diff, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_diff_", completed.states[state_i], "_123.csv")))
}

@@

age_cod_results$widened_gap <- sign(age_cod_results$age_COD_cont_yrs_mean)
age_cod_results <- make_pretty_decomp_plot(decomp.table = age_cod_results, strat.var.1 = "stratum.id",
                                           strat.var.2 = "state", strat.var.3 = "age_minbin",
                                           partition.bar.var = "COD", sign.var = "widened_gap",
                                           decomp.var = "age_COD_cont_yrs_mean", decomp.var.prop = "age_COD_prop_mean",
                                           type.of.data = "practice")

#trying to get this to work 
age_cod_results_test <- make_pretty_decomp_plot(decomp.table = subset(age_cod_results, stratum.id == "Alabama.1969.Female"), 
                                                strat.var.1 = "stratum.id",
                                           strat.var.2 = "state", strat.var.3 = "age_minbin",
                                           partition.bar.var = "COD", sign.var = "widened_gap",
                                           decomp.var = "age_COD_cont_yrs_mean", decomp.var.prop = "age_COD_cont_prop_mean",
                                           type.of.data = "results")

ggplot(data = age_cod_results_test, aes(y = age, x = start)) + geom_bar(fill = COD)

age_cod_results_test$age.n <- as.numeric(age_cod_results_test$age) #need to fix the 5 year old when convert to nummeric
    ggplotly(ggplot(age_cod_results_test,
                    aes(y = age.n, x = start)) + 
               geom_rect(aes(xmin = start, xmax = finish, ymin = age.n - 0.45, ymax = age.n + 0.45, fill = COD), col = "white") +
               #xlab(paste0("Contribution to life expectancy gap ", xaxis.title())) +
               #ylab("Age group\n") +
               theme_minimal() +
               geom_vline(xintercept = 0)  
               #facet_wrap(~ year) +
               #ggtitle(paste0(input$selected_sex, "s in ", input$state)) 
             ) 
```

@@

```{r save_combined_datasets, echo = F}
write.csv(age_cod_results_female, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_female.csv")
write.csv(age_cod_results_male, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_male.csv")
write.csv(age_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_decomp_results.csv")
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
write.csv(BlackWhite_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_results.csv")
write.csv(cod_change_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_change_results.csv")

write.csv(mortality.rates, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_combined.csv")
write.csv(mortality.rates.diff, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_diff_combined.csv")
```

>>>>

**Combine results across the sets**
The analysis was run in 3 sets of states. In this file we combine the results and tidy the data for graphing and presentation.

```{r initialize}
library(stringr)
library(dplyr)
source("./Code/life_expectancy_functions.R")
```

```{r}
included.states <- c("Alabama", "Arizona", "Arkansas", "California", "Colorado", "Connecticut",
"Delaware", "Florida", "Georgia", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky",
"Louisiana", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi",   
"Missouri", "Nebraska", "Nevada", "New Jersey", "New Mexico", "New York",
"North Carolina", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island",
"South Carolina",  "Tennessee", "Texas", "Virginia", "Washington", "Washington DC",
"West Virginia", "Wisconsin") 
```

```{r combine_results_seed123}
age_cod_results <- read.csv(paste0("./Results2/age_cod_", included.states[1], "_123.csv"))
age_decomp_results <- read.csv(paste0("./Results2/age_decomp_", included.states[1], "_123.csv"))
BlackWhite_results <- read.csv(paste0("./Results2/BlackWhite_", included.states[1], "_123.csv"))
cod_decomp_results <- read.csv(paste0("./Results2/cod_marginal_", included.states[1], "_123.csv"))
cod_change_results <- read.csv(paste0("./Results2/cod_change_", included.states[1], "_123.csv"))

mortality.rates <- read.csv(paste0("./Results2/mortality_rates_", included.states[1], "_123.csv"))
mortality.rates.diff <- read.csv(paste0("./Results2/mortality_rates_diff_", included.states[1], "_123.csv"))

for(state_i in 2:length(included.states)){

    age_cod_results <- rbind(age_cod_results, read.csv(paste0("./Results2/age_cod_", included.states[state_i], "_123.csv")))

    age_decomp_results <- rbind(age_decomp_results, read.csv(paste0("./Results2/age_decomp_", included.states[state_i], "_123.csv")))

    BlackWhite_results <- rbind(BlackWhite_results, read.csv(paste0("./Results2/BlackWhite_", included.states[state_i], "_123.csv")))

    cod_decomp_results <- rbind(cod_decomp_results, read.csv(paste0("./Results2/cod_marginal_", included.states[state_i], "_123.csv")))    
    cod_change_results <- rbind(cod_change_results, read.csv(paste0("./Results2/cod_change_", included.states[state_i], "_123.csv")))    
    mortality.rates <- rbind(mortality.rates, read.csv(paste0("./Results2/mortality_rates_", included.states[state_i], "_123.csv")))

    mortality.rates.diff <- rbind(mortality.rates.diff, read.csv(paste0("./Results2/mortality_rates_diff_", included.states[state_i], "_123.csv")))
}

@@

age_cod_results$widened_gap <- sign(age_cod_results$age_COD_cont_yrs_mean)
age_cod_results <- make_pretty_decomp_plot(decomp.table = age_cod_results, strat.var.1 = "stratum.id",
                                           strat.var.2 = "state", strat.var.3 = "age_minbin",
                                           partition.bar.var = "COD", sign.var = "widened_gap",
                                           decomp.var = "age_COD_cont_yrs_mean", decomp.var.prop = "age_COD_prop_mean",
                                           type.of.data = "practice")
```

@@

```{r save_combined_datasets, echo = F}
write.csv(age_cod_results_female, "./Results2/age_cod_results_female.csv")
write.csv(age_cod_results_male, "./Results2/age_cod_results_male.csv")
write.csv(age_decomp_results, "./Results2/age_decomp_results.csv")
write.csv(cod_decomp_results, "./Results2/cod_decomp_results.csv")
write.csv(BlackWhite_results, "./Results2/BlackWhite_results.csv")
write.csv(cod_change_results, "./Results2/cod_change_results.csv")
write.csv(mortality.rates, "./Results2/mortality_rates_combined.csv")
write.csv(mortality.rates.diff, "./Results2/mortality_rates_diff_combined.csv")
```
